Copyright

### 2025-07-09 choose_license.qmd
Reformat code and fix typos

- The license of embedded elements (e.g., images) is either given
  directly beneath to where they are embedded,
  at the end of the respective page,
  or collectively on an separate page.

@@

The manuscript and the bibliography file you downloaded for this tutorial
are made available to you under [CC0\ 1.0][cc0]
as is all code in this tutorial (e.g., for the data analysis).
Therefore, you can apply any license to your modified version.
Please apply the license of your choice now,
using any of the methods mentioned above (except the `README`, which we will cover later).

@@

Note. DRM = digital rights management

@@

>>>>

- The license of embedded elements (e.g., images) is either given
  directly beneath to where they are embedded,
  at the end of the respective page,
  or collectively on a separate page.

@@

The manuscript and the bibliography file you downloaded for this tutorial
are made available to you under [CC0\ 1.0][cc0]
as is all code in this tutorial (e.g., for the data analysis).
Therefore, you can apply any license to your modified version.
Please apply the license of your choice now,
using any of the methods mentioned above (except the `README`,
which we will [cover later](make_readme.qmd)).

@@

_Note._ DRM = digital rights management

@@

_Note._ DRM = digital rights management

### 2025-07-09 copyright.qmd
Reformat code and fix typos

- Different parts of a work may be available under different licenses:
  A document may incorporate direct quotes or images by others.
  In this case, the license of the document may not cover those.
  In the best case, the authors indicate which parts of the work are covered by which license.
- A work may be available under different licenses at the choice of the (re-)user.
  This is also called multi-licensing.
  For example, authors might allow to user a work under any version of a license.
- In contrast, it may also be the case that one has to comply
  with the conditions of multiple licenses at the same time.
  This is the case, for example, if a derivative work is published
  under a different license than the original work.
:::

If you cannot find any license, the work might be
in the public domain^[in Germany: _Gemeinfreiheit_] depending on national law.
For example, the work may not cross the [threshold of originality][commons-threshold],
it may not [qualify for copyright protection][commons-unprotected]
-- such as official works by the government --,
or the copyright protection might have expired.
According to the [Berne convention][berne-convention],
copyright expires at earliest 50 years after the author's death,
but in [many countries][commons-pd] it expires even later
-- you can use a [public domain calculator][pd-calc] to check.
If no license notice is present and the work is not in the public domain,
it is _in copyright_ and you are generally not allowed to share it with others.
You can, however, ask the author to put the corresponding work under a free/open license
-- Wikimedia Commons provides an [email template][commons-templates] to obtain such a permission.
Without permission you can check you national laws
for limitations and exceptions to copyright.^[in Germany: _Schranken des Urheberrechts_]
Examples include the right to quote, [trivial use][commons-minimis],
and the US-American [fair use][wiki-fair-use].

@@

[cc-v1]: https://creativecommons.org/weblog/entry/3476
[cc-v2]: https://creativecommons.org/weblog/entry/4216#:~:text=Share%20Alike%20Across%20Borders
[cc-v3]: https://creativecommons.org/weblog/entry/7249#:~:text=BY-SA%20%E2%80%94%20Compatibility%20Structure%20Now%20Included
[cc-v4]: https://creativecommons.org/weblog/entry/40768
[cc0-v1]: http://www.creativecommons.org/weblog/entry/13304
[cc-versions]: https://wiki.creativecommons.org/wiki/License_Versions
[commons-trolls]: https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling

>>>>

- Different parts of a work may be available under different licenses:
  A document may incorporate direct quotes or images by others.
  In this case, the license of the document may not cover those.
  In the best case, the authors indicate which parts of the work are covered by which license.
- A work may be available under different licenses at the choice of the (re-)user.
  This is also called multi-licensing.
  For example, authors might allow to use a work under any version of a license.
- In contrast, it may also be the case that one has to comply
  with the conditions of multiple licenses at the same time.
  This is the case, for example, if a derivative work is published
  under a different license than the original work.
:::

If you cannot find any license, the work might be
in the public domain^[in Germany: _Gemeinfreiheit_] depending on national law.
For example, the work may not cross the [threshold of originality][commons-threshold],
it may not [qualify for copyright protection][commons-unprotected]
-- such as official works by the government --,
or the copyright protection might have expired.
According to the [Berne convention][berne-convention],
copyright expires at earliest 50 years after the author's death,
but in [many countries][commons-pd] it expires even later
-- you can use a [public domain calculator][pd-calc] to check.
If no license notice is present and the work is not in the public domain,
it is _in copyright_ and you are generally not allowed to share it with others.
You can, however, ask the author to put the corresponding work under a free/open license
-- Wikimedia Commons provides an [email template][commons-templates] to obtain such a permission.
Without permission you can check your national laws
for limitations and exceptions to copyright.^[in Germany: _Schranken des Urheberrechts_]
Examples include the right to quote, [trivial use][commons-minimis],
and the US-American [fair use][wiki-fair-use].

@@

[cc-v1]: https://creativecommons.org/weblog/entry/3476
[cc-v2]: https://creativecommons.org/weblog/entry/4216#:~:text=Share%20Alike%20Across%20Borders
[cc-v3]: https://creativecommons.org/weblog/entry/7249#:~:text=BY-SA%20%E2%80%94%20Compatibility%20Structure%20Now%20Included
[cc-v4]: https://creativecommons.org/weblog/entry/40768
[cc0-v1]: https://www.creativecommons.org/weblog/entry/13304
[cc-versions]: https://wiki.creativecommons.org/wiki/License_Versions
[commons-trolls]: https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling
